### 2022-04-08 sections/papers.tex
Update papers.tex

\item{Orchard, X., \& González-Bustamante, B. ({\itshape forthcoming}). Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019). {\itshape The International Journal of Press/Politics}.}

@@

\begin{benumerate}{10}
\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. ({\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. Introduction. {\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}

>>>>

\item{Orchard, X., \& González-Bustamante, B. (2022). Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019). {\itshape The International Journal of Press/Politics}. Online First. {\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}}\vspace{1mm}

@@

\begin{benumerate}{12}
\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. ({\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. Introduction. {\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2021). Sophistication, Participation, and Political Engagement in Latin America. {\itshape Tufte Working Papers}, 2, 1--21. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C. (2020).  Applying ForceAtlas2, a Continuous Graph Layout Algorithm, to the Elites Study. {\itshape Tufte Working Papers}, 1, 1--15. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}
